In-silico molecular enrichment and clearance of the human intracranial space

### 2024-12-19 paper/supplementary_main.tex
Clean-up Dispersion in Methods - moving to the Supplementary.

@@

Further assuming unsteady dispersion, we follow Sharp et al \cite{keith2019dispersion} and estimate each enhancement factor $R_{\rm cardiac}$ and $R_{\rm resp}$ from the non-dimensionalized pressure gradient 
$$R_{i} \approx dP_{i}^2 / \alpha_{i}^3, \quad  \text{where} \quad  dP=\frac{|\nabla p^{\rm up}_{i}|}{\omega_{i} \mu / h} \quad \text{for} \quad i = \{\mathrm{cardiac}, \mathrm{resp}\}.$$
Finally, we account for the non-local nature of the dispersion mechanism and smooth the resulting field by solving a Helmholtz problem with $dP+i^2/\alpha_i^3$ as the right-hand side
\begin{equation}
- 10^{-4} \Delta R_i + R_i = dP_i^2/\alpha_i^3 \quad \text{ on } \Omega_{\rm CSF} \qquad \text{ and } \quad \nabla R_i \cdot \bm n = 0, \quad \text{ on } \partial \Omega_{\rm CSF}
\end{equation}
to obtain the locally averaged, spatially varying diffusion enhancement factor $R_i$. The diffusion enhancement factor $R$ in $D^{\mathrm{eff}} = D^{\mathrm{Gad}}( 1 +R)$ is then estimated by $R \approx R_{\rm{cardiac}} + R_{\rm{resp}}$. 
% %\subsubsection{Cardiac Dispersion Factor Estimation}
% %\label{sec:dispersion_details}

>>>>

\mer{MER: Moved the below from Results.}
\mar{To examine cardiac-driven dispersion, we compute a steady CSF flow field at peak systolic blood inflow. We mimic the resulting reduction of CSF space volume by imposing an inflow of $6\,$ml/s \cite{baledent2014imaging, causemann2022human} and $0.31\,$ml/s \cite{vinje2019respiratory} across the upper arachnoid mater ($\Gamma_{\rm AM-U}$) and the lateral ventricle ($\Gamma_{\rm LV}$) surface, respectively. We allow free outflow into the spinal SAS ($\Gamma_{\rm SSAS}$). In addition, we upscale the obtained pressure field to account for the lack of pulsatile inertial effects in our model (see \Cref{sec:csf_dispersion}).}

% respiratory pulsatility
\mar{Employing the same methodology, we estimate the respiratory contribution to dispersive mixing by computing the CSF flow field driven by an inflow of $0.121\,$ml/s \cite{liu2024using} and $1\,$ml/s \cite{gutierrez2022effect} across the lateral ventricular wall and the arachnoid mater, respectively.}

@@

Further assuming unsteady dispersion, we follow Sharp et al \cite{keith2019dispersion} and estimate each enhancement factor $R_{\rm cardiac}$ and $R_{\rm resp}$ from the non-dimensionalized pressure gradient 
$$R_{i} \approx dP_{i}^2 / \alpha_{i}^3, \quad  \text{where} \quad  dP=\frac{|\nabla p^{\rm up}_{i}|}{\omega_{i} \mu / h} \quad \text{for} \quad i = \{\mathrm{cardiac}, \mathrm{resp}\}.$$
Finally, we account for the non-local nature of the dispersion mechanism and smooth the resulting field by solving a Helmholtz problem with $dP+i^2/\alpha_i^3$ as the right-hand side
\begin{equation}
- 10^{-4} \Delta R_i + R_i = dP_i^2/\alpha_i^3 \quad \text{ on } \Omega_{\rm CSF} \qquad \text{ and } \quad \nabla R_i \cdot \bm n = 0, \quad \text{ on } \partial \Omega_{\rm CSF}
\end{equation}
to obtain the locally averaged, spatially varying diffusion enhancement factor $R_i$. The diffusion enhancement factor $R$ in $D^{\mathrm{eff}} = D^{\mathrm{Gad}}( 1 +R)$ is then estimated by $R \approx R_{\rm{cardiac}} + R_{\rm{resp}}$.

% %\subsubsection{Cardiac Dispersion Factor Estimation}
% %\label{sec:dispersion_details}
